### 2019-01-25 manuscript.tex
Update manuscript.tex

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would
expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15 were reported by their mothers. The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18). The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not
academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}. Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
progress is hindered due to the complicated history of the very practice. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, KhosBane17, SchuLien13, WHO12}. Interventions based on associating FGC with violations
of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position. This paragraph is to briefly present fgc in context.}

@@

pricking \cite{WahlJohn17a, WahlJohn17b}

>>>>

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would
expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15 were reported by their mothers. The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).  United Nation has declared zero tolerance for FGC as it violates human rights and promoted the abundance of the practice  \cite{}.  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see
http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not
academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}. Breaking with the tradition can be salvaging even after migration \cite{CreiSamu19, PariSaru18, WahlJohn17a}.  FGC is also known as female genital mutilation and female circumcision;
we use cutting instead because it implies a degree of self-awareness and is considered less judgmental \cite{KhahBark09, JohnEsse10,
Meye00, PariSaru18, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the
progress is hindered due to the complicated history of the very practice \cite{cite}. The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to cultural and religious identity in one end and to public health and human rights on the other \cite{Boyl02, KhosBane17, KimaShell18, SchuLien13, WHO12}.  In addition, interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{Obio97, MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, GaluKama15, JohnEsse10, WahlEsse18}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position. This paragraph is to briefly present fgc in context.}

@@

Suggestions: pricking (type IV\cite{WHO08})\cite{WahlJohn17a, WahlJohn17b} and medical FGC \cite{KimaShell18} vs. no-tolerance, fgc vs. mc \cite{WahlEsse18}?
